A Control Strategy for a Tethered Follower Robot for Pulmonary Rehabilitation

### 2020-04-10 alpibot.tex
Agrego los agradecimientos.

\author{Bianchi Luciano, Buzniak Esteban, Ramele~Rodrigo,~\IEEEmembership{Member,~IEEE,}
        and Santos~Juan~Miguel% <-this % stops a space
\thanks{R. Ramele  and J.M.Santos are with the Department
of  Computer Engineering, Instituto Tecn{o'}gico de Buenos Aires (ITBA), Ciudad de Buenos Aires,  Argentina e-mail: rramele@itba.edu.ar}% <-this % stops a space
\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}

@@

% use section* for acknowledgment
\section{Acknowledgments}
This project was supported by ALPI organization.

>>>>

\author{Bianchi Luciano, Buzniak Esteban, Ramele~Rodrigo,~\IEEEmembership{Member,~IEEE,}
        and Santos~Juan~Miguel% <-this % stops a space
\thanks{E. Buzniak, R. Ramele  and J.M.Santos are with the Department
of  Computer Engineering, Instituto Tecn{o'}gico de Buenos Aires (ITBA), Ciudad de Buenos Aires,  Argentina e-mail: rramele@itba.edu.ar}% <-this % stops a space
\thanks{Manuscript received April 19, 2020; revised August 26, 2015.}}

@@

% use section* for acknowledgment
\section{Acknowledgments}
This project is part of a joint collaboration between ALPI organization and the ITBA University.  Authors would like to thank thoughtfully for their initiative, support given by the ALPI organization.  Specially to Natalia Nerina Meda, Soledad Suriá, Eduardo Etcheverry and Sergio Carlos Franco, for their invaluable help and enthusiasm to move this project forward.
